$3$-D Weak Lensing Mass Map Reconstruction: Reducing the line of sight smearing

### 2020-12-07 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex
correct many typos

\begin{figure*}
\centering
\subfigure[NFW: $\lambda=3.5$]{
        \includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}
    }
\subfigure[NFW: $\lambda=5.0$]{\includezraphics{
        delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}
    }
\caption{The density maps reconstructed from the mock galaxy shape catalog with
    the NFW dictionary. The penalization parameters are $\lambda=3.5$ (left)
    and $\lambda=5.0$ (right).  The input halo mass is $M_{200}=10^{15.02}
    ~h^{-1}M_{\odot}$, and its redshift is $z=0.164$.  The vertical direction
    is the line of sight direction. The boxes' lower boundaries and upper
    boundaries of correspond to $z=0.01$ and $z=0.85$, respectively.
    } \label{fig_NFW3D}
\end{figure*}

In this subsection, we test the performance of our algorithm with the default
setup that models the matter density field with multi-scale NFW atoms. The
dictionary is constructed with three frames of different NFW scale radii in the
comoving coordinate: $0.12~h^{-1}$ Mpc, $0.24~h^{-1}$ Mpc, and $0.36~h^{-1}$
Mpc.  The truncation radii are set to four times the comoving scale radii for
the atoms in the dictionary (concentration equals four) . We note that each
frame of our dictionary fixes the scale radius in the comoving space;
therefore, the NFW atoms have different angular radii in different lens
redshift bins.

We test the algorithm with different regularization parameters ($\lambda$) for
the preliminary lasso estimation, which are $3.5$, $4.0$, and $5.0$. The
corresponding regularization parameters for the final adaptive lasso estimations
are set to $\lambda_{\rm{ada}}=\lambda^{\tau+1}$.  Here, we note that both the
preliminary lasso estimation and the final adaptive lasso estimation select the
pixels with the signal-to-noise ratios (SNRs) greater than $\lambda$ in each
gradient descent iteration. While the final adaptive lasso estimation further
enhances the growth of the pixels with preliminary estimations greater than
$\lambda$.

@@

Figure \ref{fig_NFW3D} shows the $3$-D density maps reconstructed with
different penalization parameters for a halo with $M_{200}=10^{15.02}
~h^{-1}M_{\odot}$ at redshift $0.164$.  As we can see from the reconstructed
density maps, the adaptive lasso algorithm sets most of the reconstructed
pixels to zero and only keeps the pixels with large amplitudes.  We identify
the peaks on the reconstructed sparse density map.

>>>>

\begin{figure*}[!t]
\begin{minipage}[c]{1.0\columnwidth}
\includegraphics[width=0.95\textwidth]{pixel_histograms_halo17_NFW_lbd35.pdf}
    \includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}
    \centering
    \small NFW: $\lambda=3.5$
\end{minipage}
\begin{minipage}[c]{1.0\columnwidth}
\includegraphics[width=0.95\textwidth]{pixel_histograms_halo17_NFW_lbd50.pdf}
    \includezraphics{delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}
    \centering
    \small
    NFW: $\lambda=5.0$
\end{minipage}
\caption{The lower panels show the density maps reconstructed from the mock
    galaxy shape catalog with the NFW dictionary. The upper panels show the
    pixels' number histograms.  The penalization parameters are $\lambda=3.5$
    (left) and $\lambda=5.0$ (right).  The input halo mass is
    $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$, and its redshift is $z=0.164$.  The
    vertical direction is the line of sight direction. The boxes' lower
    boundaries and upper boundaries of correspond to $z=0.01$ and $z=0.85$,
    respectively.
    } \label{fig_NFW3D}
\end{figure*}

In this subsection, we test the performance of our algorithm with the default
setup that models the matter density field with multi-scale NFW atoms. The
dictionary is constructed with three frames of different NFW scale radii in the
comoving coordinate: $0.12~h^{-1}$ Mpc, $0.24~h^{-1}$ Mpc, and $0.36~h^{-1}$
Mpc.  The truncation radii are set to four times the comoving scale radii for
the atoms in the dictionary (concentration equals four) . We note that each
frame of our dictionary fixes the scale radius in the comoving coordinates;
therefore, the NFW atoms have different angular radii in different lens
redshift bins.

We test the algorithm with different regularization parameters ($\lambda$) for
the preliminary lasso estimation, which are $3.5$, $4.0$, and $5.0$. The
corresponding regularization parameters for the final adaptive lasso
estimations are set to $\lambda_{\rm{ada}}=\lambda^{\tau+1}$.  Here, we note
that both the preliminary lasso estimation and the final adaptive lasso
estimation select the pixels with the signal-to-noise ratios (SNRs) greater
than $\lambda$ in each gradient descent iteration and estimate the density in
the selected pixels. While the final adaptive lasso estimation further enhances
the growth of the pixels with preliminary estimations greater than $\lambda$.

@@

Figure \ref{fig_NFW3D} shows the $3$-D density maps reconstructed with
different penalization parameters for a halo with $M_{200}=10^{15.02}
~h^{-1}M_{\odot}$ at redshift $0.164$. Also, the pixels' histograms are shown
in Figure \ref{fig_NFW3D}. From these plots, we conclude that the adaptive
lasso algorithm sets most of the reconstructed pixels to zero and only keeps
the modes strongly related to the data. Moreover, the reconstructed density maps
do not suffer from the line of sight smearing. After the reconstruction for
each simulation, we identify the peaks on the sparse density map.
